---
title: "Covid19: The Battle For Independence Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Covid19: The Battle For Independence Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19BFI)
```

# **covid19BFI**

The R package _covid19BFI_ is a container for the _"Covid19: The Battle of Independence""_ whoch is an application that has been built as an interactive comparative tool for the analysis over the impact and response to corona virus between Ireland and the United Kingdom. As detailed in the _"About"_ section, there is a long standing and divisive history of conflict and war between the two countries that stems from Ireland's plight for seeking their complete independence from the United Kingdom. Corona virus has presented pundits who are pro independence  with a case study to further ignite and push the fight for independence, with the difference in impact and response between Ireland and the United Kingdom acting as a proxy for Ireland's ability to stand completely independent, with this package providing access to the application that hands
the user the data and the tools to make critically assess the responses between the two countries as well, as access the data and other tools to recreate the analysis.

## Launching the _Covid19: The Battle for Independence_ application

Tha application can be accessed by using the **launch_app( )** function provided by the _covid19BFI_ package. When run, **launch_app** will build and generate the _Covid19: The Battle for Independence_ application.

## What _Covid19: The Battle for Independence_ application provides

The application has been built as an interactive comparative tool to assess the different impact and response that Ireland and the United Kingdom (GBR) have taken with regards to dealing with covid19. This application provides four web pages that the user can navigate across by accessing the navigation bar that can be found along the top border of the app. The navigation bar list four separate sections, they are:

  1. _About_ 
  2. _Cases, Deaths and Government Intervention_
  3. _Movement Analysis_
  4. _References and acknowledgements_

The analysis that can be found in the indvidual sections and their interactive features are detailed below:

  - **About**: Contains information regarding purpose and basis behind the application as well as information regarding the creator of the application.
  
  - **Cases Deaths and Government Intervention**: Contains an interactive comparitive analysis on the each of the following statistics: 
  
    - Cumulative Confirmed Cases per capita, 100,000
    - Daily Death Total per capita, 100, 000
    - Cumulative Death per capita, 100,000
    - Daily Confirmed Cases
    - Cumulative Deaths
    - Daily Confirmed Deaths
    - Daily Confirmed Cases per capita, 100,000
    - Log of Cumulative Confirmed Cases
    - Log of Daily Confirmed Cases
    - Log of Cumulative Deaths
    - Social distancing measures
    - Movement Restrictions
    - Public Health Measures
    
    - The page displays an interactive figure visualising the selected counts that have been chosen for comparison between the two nations and a table comparing the different number of measures used by each governemnt across the dates they were implemented. Futhermore, an interactive table is presented which provides a grouped monthly percentage breakdown across the number of measures, restrictions and policies enacted by both Ireland and United Kingdom for the following three types of government intervention:

      1. _Number of social distance measures_
      2. _Number of movement restrictions_
      3. _Number of introduced public health policies_
  
    - Here the user can you navigate across the percentage breakdown of the three types of government intervention by accessing tabs that are situated below the the heading "Government intervention" for both countries, with the United Kingdom (GBR) colored red and Ireland colored in green.
        
  - **Movement Analysis**: This page provides an analysis on the impact of covid19 has had on the mobility of residents of the major cities in both Ireland and the United Kingdom. The page displays a map of both Ireland and the United Kingdom with the major citites highlights and figure displaying the movement trends of residents in the following three forms of transport: 
      1. driving 
      2. transit 
      3. walking, 
    as recorded by the apple maps usage fo each of those forms of transportation. This page contains the following interactive elements:
        1. The majoy cities displayed on the map for both countries can be clicked in order to update plot below which is a figure displaying the change in driving, walking and transit use during the pandemic. 
    - The side bar contains two options:
        1. A drop down menu which allows the user to select the country they wish to focus on
        2. A drop down menu that allows them to manually update the figure with the city of their choice, to assess the change in transport use
    - thus providing the user with the ability to take an in-depth look at the impact and timing that the government intervention with corona virus has had on mobility across the key cities of both countries to make an assessment of whether or not the appropriate action was taken as can be now deemed as required.
        
## Features of the _covid19BFI_ package

Along with the access the application 
